AMORPH: A statistical program for characterizing amorphous materials by X-ray diffraction

### 2017-09-09 doc/ms.tex
Arxivable formatting
Removed journal name
Updated references
Geometry tweak
Couple of minor edits

\documentclass[review]{elsarticle}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
% \usepackage[left=2cm, right=2cm, bottom=3cm, top=2cm]{geometry}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{pdflscape}
\usepackage{gensymb} % For degree symbol
\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Computers and Geosciences}

@@

\linenumbers

@@

\section{Applications}\label{sec:applications}
\subsection{Crystallinity}
The AMORPH program calculates a fraction of amorphous material ($A_{\rm m}$) for each posterior sample of the parameters,
using Equation~\ref{eqn:crystallinity}.Thus measured crystallinity ($C_{\rm m}$) is easily determined from the relationship $C_{\rm m}$ = 1-$A_{\rm m}$, as defined in Equation 5. The measured crystallinity is not equivalent to an "actual" or "true" crystallinity, although the values are often very close to one another.
It should therefore be noted that this procedure does not negate the need for calibration standards
to translate measured crystallinity to an actual crystallinity. Transmission and absorption of X-rays in the material will vary as the ratio of mineral to glass changes in the sample, causing a deviation from a 1:1 line. In addition to theoretical considerations, practical challenges also exist for background fitting. At low crystallinity ($\lesssim 10\%$) diffraction patterns are dominated by the low amplitude amorphous peak such that removing the effects of background noise becomes problematic, resulting in overestimated crystallinities. At high crystallinity ($\gtrsim 90\%$) the problem arises that peak overlaps in multi-mineral assemblages cause broadening effects, and may be subsequently modeled as ``amorphous'' and thus crystallinities  underestimated. The calibration curve therefore is utilized to remove these effects. This is also an important step as
different X-ray diffractometers will provide slightly different calibration curves (Fig.~\ref{fig:intruments}).
Differences between instruments largely reflect changes in background intensity and shape,
particularly at low values of $2\theta$.

@@

\bibitem[Brewer et al.(2011)]{dns}
Brewer, B. J., Pártay, L. B., \& Csányi, G. (2011). Diffusive nested sampling. Statistics and Computing, 21(4), 649-656.

\bibitem[{Brewer} and {Foreman-Mackey}(2016)]{dnest4}
Brewer, B. J., Foreman-Mackey, D.
\newblock {DNest4: Diffusive Nested Sampling in C++ and Python}.
\newblock \emph{Journal of Statistical Software, accepted. arxiv: 1606.03757},
  June 2016.

@@

\bibitem[Gregory(2005)]{gregory2005bayesian}
Gregory, P. C.
\newblock \emph{Bayesian Logical Data Analysis for the Physical Sciences: A
  Comparative Approach with Mathematica{\textregistered} Support}.
\newblock Cambridge University Press, 2005.

@@

\bibitem[Knuth and Skilling(2012)]{knuth2012foundations}
Knuth, K. H., Skilling, J.
\newblock Foundations of inference.
\newblock \emph{Axioms}, 1\penalty0 (1):\penalty0 38--73, 2012.

@@

\bibitem[Mackay(2003)]{mackay2003}
MacKay, D. J. C. (2003). Information theory, inference and learning algorithms. Cambridge university press.

@@

\bibitem[O'Hagan and Forster(2004)]{o2004kendall}
O'Hagan, A., Forster, J. J.
\newblock \emph{Kendall's advanced theory of statistics, volume 2B: Bayesian
  inference}, volume~2.
\newblock Arnold, 2004.

@@

\bibitem[Schmidt et al.(2009)]{schmidt2009}
Schmidt, M. E. et al. 2009. Spectral, mineralogical, and geochemical variations across Home Plate, Gusev Crater, Mars indicate high and low temperature alteration. Earth Planet. Sci. Lett. 281, 258–268.

\bibitem[Sivia and Skilling(2006)]{sivia2006data}
Sivia, D., Skilling, J.
\newblock \emph{Data analysis: a Bayesian tutorial}.
\newblock OUP Oxford, 2006.

>>>>

\documentclass[preprint, a4paper]{elsarticle}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[left=2.2cm, right=2.2cm, bottom=3cm, top=2.5cm]{geometry}
\usepackage{microtype}
\usepackage{natbib}
\usepackage{pdflscape}
\usepackage{gensymb} % For degree symbol
%\usepackage{lineno,hyperref}
%\modulolinenumbers[5]

\journal{}

@@

%\linenumbers

@@

\section{Applications}\label{sec:applications}
\subsection{Crystallinity}
The AMORPH program calculates a fraction of amorphous material ($A_{\rm m}$) for each posterior sample of the parameters,
using Equation~\ref{eqn:crystallinity}. Thus, measured crystallinity ($C_{\rm m}$) is easily determined from the relationship $C_{\rm m} = 1-A_{\rm m}$, as defined in Equation 5. The measured crystallinity is not equivalent to an ``actual'' or ``true'' crystallinity, although the values are often very close to one another.
It should therefore be noted that this procedure does not negate the need for calibration standards
to translate measured crystallinity to an actual crystallinity. Transmission and absorption of X-rays in the material will vary as the ratio of mineral to glass changes in the sample, causing a deviation from a 1:1 line. In addition to theoretical considerations, practical challenges also exist for background fitting. At low crystallinity ($\lesssim 10\%$) diffraction patterns are dominated by the low amplitude amorphous peak such that removing the effects of background noise becomes problematic, resulting in overestimated crystallinities. At high crystallinity ($\gtrsim 90\%$) the problem arises that peak overlaps in multi-mineral assemblages cause broadening effects, and may be subsequently modeled as ``amorphous'' and thus crystallinities  underestimated. The calibration curve therefore is utilized to remove these effects. This is also an important step as
different X-ray diffractometers will provide slightly different calibration curves (Fig.~\ref{fig:intruments}).
Differences between instruments largely reflect changes in background intensity and shape,
particularly at low values of $2\theta$.

@@

\bibitem[Brewer et al.(2011)]{dns}
Brewer, B. J., Pártay, L. B., \& Csányi, G. 2011. Diffusive nested sampling. Statistics and Computing, 21(4), 649-656.

\bibitem[{Brewer} and {Foreman-Mackey}(2016)]{dnest4}
Brewer, B. J., Foreman-Mackey, D. 2016.
\newblock {DNest4: Diffusive Nested Sampling in C++ and Python}.
\newblock \emph{Journal of Statistical Software, accepted. arxiv: 1606.03757}.

@@

\bibitem[Gregory(2005)]{gregory2005bayesian}
Gregory, P. C. 2005.
\newblock \emph{Bayesian Logical Data Analysis for the Physical Sciences: A
  Comparative Approach with Mathematica{\textregistered} Support}.
\newblock Cambridge University Press, 468pp.

@@

\bibitem[Knuth and Skilling(2012)]{knuth2012foundations}
Knuth, K. H., Skilling, J. 2012.
\newblock Foundations of inference.
\newblock Axioms, 1\penalty0 (1), \penalty0 38--73.

@@

\bibitem[Mackay(2003)]{mackay2003}
MacKay, D. J. C. 2003. Information theory, inference and learning algorithms. Cambridge University Press, 628pp.

@@

\bibitem[O'Hagan and Forster(2004)]{o2004kendall}
O'Hagan, A., Forster, J. J. 2004.
\newblock \emph{Kendall's advanced theory of statistics, volume 2B: Bayesian
  inference}, volume~2.
\newblock Arnold, 496pp.

@@

\bibitem[Schmidt et al.(2009)]{schmidt2009}
Schmidt, M. E. et al. 2009. Spectral, mineralogical, and geochemical variations across Home Plate, Gusev Crater, Mars indicate high and low temperature alteration. Earth and Planetary Science Letters, 281, 258–268.

\bibitem[Sivia and Skilling(2006)]{sivia2006data}
Sivia, D., Skilling, J. 2006.
\newblock \emph{Data analysis: a Bayesian tutorial}.
\newblock Oxford University Press, 246pp.
